---
params:
  type: "monthly"
  default_date: "2026-01-02 00"
  monitor_groups: 
    - "FEM and PA"
    - "FEM" 
    - "PA" 
  dirs:
    value:
      data: data
      plots: plots
      lib: libs
  run_current: false
  report: !expr source("../R/set_params.R"); set_params(type = "monthly", default_report_date = "2026-01-02 00")
title: "Canadian PM~2.5~ Observations Monthly Summary for <mark class='bg-info'>`r params$report$display_name`</mark>"
subtitle: | 
  Non-validated, auto-QA/QCed data representing `r params$report$date_ranges$utc`<br>
  `r params$report$date_ranges$vancouver` in Vancouver |
  `r params$report$date_ranges$halifax` in Halifax
date: "`r params$report$date`"
citation: 
  id: monthly-report
  title: "Monthly Canada PM2.5 Summary: {RNAME}"
  url: https://aqmap.ca/aqmap/reports/monthly/historic/{RFILE}.html
  publisher: "University of Northern British Columbia, Environment and Climate Change Canada"

format:
  html:
    pagetitle: "Monthly Canada PM2.5 Summary"
---

<meta name="viewport" content="width=device-width, initial-scale=1">

```{r setup}

source("R/report-functions.R")
source("R/report-constants.R")

params$type |> setup_report_dirs(dirs = params$dirs)

all_monitors_group <- params$monitor_groups[1]

report_dir_esc <- params$type |> stringr::str_escape()

report_date_range <- params$type |>
  get_report_start_end(
    run_future = params$run_current,
    default_date = params$default_date |> lubridate::ymd_h(tz = "UTC")
  )

old_report_dropdown <- params$type |>
  build_report_dropdown(current_report = report_date_range[2])

obs <- report_date_range |>
  load_report_data(
    meta_cols = meta_cols,
    cache_path = file.path(params$type, "index_obs.rds"), # used when db not available
    provinces_n_territories = provinces_n_territories
  )

date_range <- range(obs$date)
output_date_fmt <- date_range[2] |> format("%Y-%m")
plot_timestamp <- date_range[2] |> format("%Y-%m")
file.path(params$type, params$dirs$plots, plot_timestamp) |> 
  dir.create(showWarnings = FALSE)
file.path(params$type, params$dirs$data, plot_timestamp) |> 
  dir.create(showWarnings = FALSE)

plot_captions <- date_range |>
  make_plot_captions(networks = params$monitor_groups)
quarto_captions <- date_range |>
  make_quarto_captions(
    monitor_groups = params$monitor_groups,
    all_monitors_group = all_monitors_group
  )

summaries <- obs |>
  make_summaries(
    type = params$type,
    fcst_zones = fcst_zones,
    monitor_groups = params$monitor_groups,
    meta_cols = meta_cols,
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    plot_timestamp = plot_timestamp
  )

```

```{r grids}

grid_xlab <- "Day of %s" |> sprintf(format(date_range[2], "%B"))

grid_data <- list(median = median, maximum = max) |>
  lapply(\(FUN) obs |> make_grid_data(FUN = FUN, type = params$type))
prov_grid_paths <- grid_data |>
  make_and_save_prov_terr_grids(
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    monitor_groups = params$monitor_groups,
    plot_timestamp = plot_timestamp,
    xlab = grid_xlab
  )

fcst_grid_data <- obs |>
  dplyr::mutate(monitor = all_monitors_group) |>
  make_grid_data(FUN = median, type = params$type, fcst_zones = fcst_zones)
fcst_grid_paths <- fcst_grid_data |>
  make_and_save_fcst_zone_grids(
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    plot_timestamp = plot_timestamp,
    xlab = grid_xlab,
    provinces_n_territories = provinces_n_territories
  )

```

```{r site_boxplots}

boxplots <- summaries$overall |>
  make_and_save_site_boxplots(
    monitor_groups = params$monitor_groups,
    date_range = date_range,
    date_format = "%Y-%m-%d",
    avg_text = "Monthly",
    plot_timestamp = plot_timestamp,
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    lib_dir = params$dirs$lib
  )

boxplot_paths <- boxplots$paths

```

```{r getNetworkCoverage}

pop_rds = "../resources/spatial/canada_gridded_pop_census_2016.rds"
# If pop rds doesnt exist
if (!file.exists(pop_rds)) {
  neg_to_zero = \(x) ifelse(x < 0, 0, x)
  # Load gridded pop. data
  pop_shp = file.path(
    "../resources/spatial/griddedPopulationCanada10km_2016_shp",
    "griddedPopulationCanada10km_2016.shp"
  )
  pop_gridded = read_sf(pop_shp) |>
    # Choose desired columns (+geometry)
    dplyr::select(total = TOT_POP2A, urban = UR_POP2A, rural = RU_POP2A) |>
    # For some reason total not always urban + rural
    # This combines urban and rural as well as any extra pop in the total column
    dplyr::mutate(total = urban + rural + neg_to_zero(total - urban - rural)) |>
    # Drop 0 pop cells
    dplyr::filter(total > 0) |>
    st_transform(crs = "WGS84")

  # Flag by prov/terr
  pt = readRDS("../resources/spatial/aqmap_selection_zones.rds")[-14] |>
    dplyr::select(prov_terr = name)
  pop_gridded = st_join(pop_gridded, pt, left = TRUE, largest = TRUE)

  # Save RDS
  saveRDS(pop_gridded, pop_rds)
} else {
  # Otherwise, just use the rds
  pop_gridded = readRDS(pop_rds)
}

# Mark cell proximity to PA/FEM
locs = summaries$monthly |>
  dplyr::ungroup() |>
  dplyr::select(monitor, lat, lng) |>
  st_as_sf(coords = c("lng", "lat"), crs = "WGS84")
pop_centers = suppressWarnings(pop_gridded |> st_centroid())
pop_gridded_coverage = pop_gridded |>
  dplyr::mutate(
    cellID = 1:n(),
    has_nearby_fem = dplyr::filter(locs, monitor == "FEM") |>
      slice(st_nearest_feature(
        pop_centers,
        dplyr::filter(locs, monitor == "FEM")
      )) |>
      st_distance(x = pop_centers, by_element = TRUE),
    has_nearby_fem = as.numeric(has_nearby_fem) < 25000,
    has_nearby_pa = dplyr::filter(locs, monitor == "PA") |>
      slice(st_nearest_feature(
        pop_centers,
        dplyr::filter(locs, monitor == "PA")
      )) |>
      st_distance(x = pop_centers, by_element = TRUE),
    has_nearby_pa = as.numeric(has_nearby_pa) < 25000,
    has_nearby_monitor = has_nearby_fem | has_nearby_pa
  )

# Summarise PA / FEM / PA+FEM coverage by prov/terr
pop_coverage = pop_gridded_coverage |>
  # Flag province region
  flag_region()
pop_coverage = pop_coverage |>
  dplyr::bind_rows(dplyr::mutate(
    pop_coverage,
    region = "Canada",
    prov_terr = "Canada"
  )) |>
  dplyr::mutate(
    region = factor(region, c("West", "Central", "East", "North", "Canada")),
    prov_terr = factor(
      prov_terr,
      c(unlist(prov_pretty), "Canada"),
      c(names(prov_pretty), "CAN")
    )
  ) |>
  data.frame() |> # drop spatial column for time saving
  # Mark cells as having nearby FEM, PA, or both
  # dplyr::group_by(cellID) |>
  # dplyr::mutate(has_nearby_fem = any(has_nearby_monitor[network == "FEM"]),
  #        has_nearby_pa = any(has_nearby_monitor[network == "PA"])) |>
  # Get pop covered/uncovered in each prov/terr by each network
  dplyr::group_by(region, prov_terr, has_nearby_fem, has_nearby_pa) |>
  dplyr::summarise(
    dplyr::across(c(total, urban, rural), \(x) sum(x, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  # Better network description
  dplyr::mutate(
    network = dplyr::case_when(
      has_nearby_fem & has_nearby_pa ~ "FEM and PA",
      has_nearby_fem ~ "FEM",
      has_nearby_pa ~ "PA",
      TRUE ~ "No Monitor"
    ) |>
      factor(c("FEM", "FEM and PA", "PA", "No Monitor"))
  ) |>
  dplyr::select(-has_nearby_pa, -has_nearby_fem) |>
  tidyr::pivot_longer(
    c(total, urban, rural),
    names_to = "pop_type",
    values_to = "pop"
  ) |>
  # dplyr::group_by(region) |>
  # tidyr::complete(prov_terr, network, pop_type) |>
  dplyr::mutate(pop = ifelse(is.na(pop), 0, pop)) |>
  # Get % coverages
  dplyr::group_by(region, prov_terr, pop_type) |>
  dplyr::mutate(
    total_pop = sum(pop, na.rm = TRUE),
    p_pop = round(pop / total_pop, 3)
  )

## FNIC coverage (First Nations and Inuit Communities == FNIC)
community_rds = "../resources/spatial/canada_communities.rds"
fnic_locs = readRDS(community_rds) |>
  dplyr::filter(type == "fnic") |>
  dplyr::select(region, prov_terr, name)

fnic_locs_coverage = fnic_locs |>
  dplyr::mutate(
    cellID = 1:n(),
    has_nearby_fem = dplyr::filter(locs, monitor == "FEM") |>
      slice(st_nearest_feature(
        fnic_locs,
        dplyr::filter(locs, monitor == "FEM")
      )) |>
      st_distance(x = fnic_locs, by_element = TRUE),
    has_nearby_fem = as.numeric(has_nearby_fem) < 25000,
    has_nearby_pa = dplyr::filter(locs, monitor == "PA") |>
      slice(st_nearest_feature(
        fnic_locs,
        dplyr::filter(locs, monitor == "PA")
      )) |>
      st_distance(x = fnic_locs, by_element = TRUE),
    has_nearby_pa = as.numeric(has_nearby_pa) < 25000,
    has_nearby_monitor = has_nearby_fem | has_nearby_pa
  )

data.table::fwrite(fnic_locs_coverage, "../../outputs/fnic_coverage.csv")

fnic_coverage = fnic_locs_coverage |>
  dplyr::bind_rows(dplyr::mutate(
    fnic_locs_coverage,
    region = "Canada",
    prov_terr = "Canada"
  )) |>
  dplyr::mutate(
    region = factor(region, c("West", "Central", "East", "North", "Canada")),
    prov_terr = factor(
      prov_terr,
      c(unlist(prov_pretty), "Canada"),
      c(names(prov_pretty), "CAN")
    )
  ) |>
  data.frame() |> # drop spatial column for time saving
  # Mark cells as having nearby FEM, PA, or both
  # dplyr::group_by(cellID) |>
  # dplyr::mutate(has_nearby_fem = any(has_nearby_monitor[network == "FEM"]),
  # has_nearby_pa = any(has_nearby_monitor[network == "PA"])) |>
  # Get fnic covered/uncovered in each prov/terr by each network
  dplyr::group_by(region, prov_terr, has_nearby_fem, has_nearby_pa) |>
  dplyr::summarise(pop = sum(rep(1, n(), na.rm = TRUE)), .groups = "drop") |>
  # Better network description
  dplyr::mutate(
    network = dplyr::case_when(
      has_nearby_fem & has_nearby_pa ~ "FEM and PA",
      has_nearby_fem ~ "FEM",
      has_nearby_pa ~ "PA",
      TRUE ~ "No Monitor"
    ) |>
      factor(c("FEM", "FEM and PA", "PA", "No Monitor"))
  ) |>
  dplyr::select(-has_nearby_pa, -has_nearby_fem) |>
  dplyr::mutate(pop_type = "fnic") |>
  # dplyr::group_by(region) |>
  # tidyr::complete(prov_terr, network, pop_type) |>
  dplyr::mutate(pop = ifelse(is.na(pop), 0, pop)) |>
  # Get % coverages
  dplyr::group_by(region, prov_terr, pop_type) |>
  dplyr::mutate(
    total_pop = sum(pop, na.rm = TRUE),
    p_pop = round(pop / total_pop, 3)
  )

coverage = dplyr::bind_rows(pop_coverage, fnic_coverage)

```

```{r coverage_charts}
fig_dims = list(h = 7, w = 9, u = 'in')

c_types = c("urban", "rural", "total", "fnic")
coverage_barcharts = lapply(c_types, \(p) {
  coverage |>
    dplyr::filter(pop_type == p) |>
    pop_coverage_barchart(p)
}) |>
  setNames(c_types)

coverage_table_paths <- paste0(
  params$type,
  "plots/",
  plot_timestamp,
  "/coverage_",
  c_types,
  "_",
  output_date_fmt,
  ".png"
) |>
  as.list() |>
  setNames(c_types)

for (ct in names(coverage_table_paths)) {
  ggsave(
    coverage_barcharts[[ct]],
    filename = coverage_table_paths[[ct]],
    dpi = 300,
    units = fig_dims$u,
    height = fig_dims$h,
    width = fig_dims$w
  )
}

# Make coverage table
coverage_table_data <- coverage |>
  dplyr::select(-total_pop) |>
  dplyr::mutate(p_pop = paste0(p_pop * 100, "%")) |>
  tidyr::pivot_wider(names_from = pop_type, values_from = c(pop, p_pop)) |>
  dplyr::arrange(region, prov_terr, network) |>
  dplyr::mutate(dplyr::across(
    c(pop_fnic, pop_rural, pop_urban, pop_total),
    \(p) format(ifelse(is.na(p), 0, p), big.mark = ",")
  )) |>
  dplyr::select(
    Region = region,
    `Prov./Terr.` = prov_terr,
    "Within 25km of" = network,
    pop_fnic,
    p_pop_fnic,
    pop_rural,
    p_pop_rural,
    pop_urban,
    p_pop_urban,
    pop_total,
    p_pop_total
  )
coverage_table = reactable(
  data = coverage_table_data,
  pagination = FALSE,
  columns = list(
    pop_fnic = reactable::colDef("Count"),
    p_pop_fnic = reactable::colDef("Percentage"),
    pop_total = reactable::colDef("Count"),
    p_pop_total = reactable::colDef("Percentage"),
    pop_rural = reactable::colDef("Count"),
    p_pop_rural = reactable::colDef("Percentage"),
    pop_urban = reactable::colDef("Count"),
    p_pop_urban = reactable::colDef("Percentage")
  ),
  columnGroups = list(
    reactable::colGroup(
      name = "FN & Inuit Communities",
      columns = c("pop_fnic", "p_pop_fnic")
    ),
    reactable::colGroup(
      name = "Total Pop. (2016)",
      columns = c("pop_total", "p_pop_total")
    ),
    reactable::colGroup(
      name = "Urban Pop. (2016)",
      columns = c("pop_urban", "p_pop_urban")
    ),
    reactable::colGroup(
      name = "Rural Pop. (2016)",
      columns = c("pop_rural", "p_pop_rural")
    )
  )
)
coverage_dl = coverage_table_data |>
  download_this(
    output_name = "network_coverage_" |>
      paste0(max(obs$date) |> format("%Y-%B")),
    output_extension = ".csv",
    sep = ",",
    dec = ".",
    button_label = "Download data as csv",
    button_type = "default",
    has_icon = TRUE,
    csv2 = FALSE,
    icon = "fa fa-save"
  )

```

```{r, maps}

# Daily Zone Summaries ----------------------------------------------------

legend_title = "Daily Mean<br>PM<sub>2.5</sub> (μg m<sup>-3</sup>)"

plot_title = paste0(
  "Animated Map of Daily Forecast Zone Mean PM~2.5~ for ",
  format(date_range[2], "%B %Y")
)
daily_zone_path = paste0(
  params$type,
  "plots/",
  plot_timestamp,
  "/fcstzone_mean_map_daily_",
  output_date_fmt,
  ".html"
)


# To add slider controls see jsfiddle.net/qs6dL200
map = make_anim_map(summaries$daily_by_zone, legend_title, height = 600)

mapview::mapshot(map, daily_zone_path, libdir = "./libs", selfcontained = FALSE)

# Monthly Zone Summaries ----------------------------------------------------

plot2_title = paste0(
  "Map of Forecast Zone Mean [left] and Max [right] for ",
  format(date_range[2], "%B %Y")
)
monthly_zone_path = paste0(
  params$type,
  "plots/",
  plot_timestamp,
  "/fcstzone_mean_map_",
  output_date_fmt,
  ".html"
)

legend_titles = list()
legend_titles$pm25 = legend_title |>
  stringr::str_replace("Daily", format(date_range[2], "%b."))
legend_titles$pm25_max = legend_titles$pm25 |>
  stringr::str_replace("Mean", "Max")

map = make_sync_map(
  summaries$monthly_by_zone,
  cols = c("pm25", "pm25_max"),
  legend_titles
)

htmltools::save_html(map, monthly_zone_path, libdir = "./libs")

```

```{r community_boxplots}

# Get data for site mean boxplots
pd = summaries$overall |>
  dplyr::bind_rows(
    summaries$overall |>
      dplyr::mutate(monitor = monitor |> unique() |> join_list_sentence()) |>
      dplyr::group_by(prov_terr, fcst_zone, nearest_community, monitor) |>
      dplyr::summarise(
        n_hours_above_30 = max(n_hours_above_30, na.rm = TRUE),
        n_hours_above_60 = max(n_hours_above_60, na.rm = TRUE),
        n_hours_above_100 = max(n_hours_above_100, na.rm = TRUE),
        pm25_mean = mean(pm25_mean, na.rm = TRUE),
        pm25_max = max(pm25_max, na.rm = TRUE),
        n_sites = sum(n_sites, na.rm = TRUE)
      )
  ) |>
  dplyr::mutate(aqhi_p_mean = aqhi_p(pm25_mean)) |>
  dplyr::full_join(expand.grid(
    prov_terr = provinces_n_territories,
    monitor2 = params$monitor_groups,
    date_max = unique(summaries$overall$date_max)
  )) |>
  dplyr::mutate(date = date_max)
# Make paths to files for saving plots
community_boxplot_paths = paste0(
  params$type,
  "plots/",
  plot_timestamp,
  "/communities_veryHigh_hours_",
  params$monitor_groups |>
    stringr::str_to_lower() |>
    stringr::str_replace_all(" ", "_"),
  '_',
  output_date_fmt,
  ".html"
) |>
  setNames(params$monitor_groups) |>
  as.list()
# MAke and save plots
.tmp = lapply(params$monitor_groups, \(m) {
  pd |>
    subset(monitor == m) |>
    make_community_boxplots(m, date_range = date_range) |>
    htmlwidgets::saveWidget(
      community_boxplot_paths[[m]],
      libdir = "./libs",
      selfcontained = FALSE
    )
}) |>
  setNames(params$monitor_groups)

```

```{r worst_day_tables}
# Make download link and table for province level
worst_day_dl = summaries$worst_day |>
  setNames(names(summaries$worst_day) |> stringr::str_replace_all("\n", " ")) |>
  download_this(
    output_name = "worst_days_by_provterr_" |>
      paste0(max(obs$date) |> format("%Y-%B")),
    output_extension = ".csv",
    sep = ",",
    dec = ".",
    button_label = "Download data as csv",
    button_type = "default",
    has_icon = TRUE,
    csv2 = FALSE,
    icon = "fa fa-save"
  )
worst_day_table = reactable(
  data = summaries$worst_day,
  pagination = FALSE,
  defaultSorted = "Mean of Site Means",
  defaultSortOrder = "desc",
  columnGroups = list(
    reactable::colGroup(
      name = "PM2.5 Concentration (ug/m3)",
      columns = c(
        "Min of Site Means",
        "Mean of Site Means",
        "Max of Site Means"
      )
    )
  )
)

# Make download link and table for fcst zone level
pd = summaries$daily |>
  dplyr::group_by(nearest_community, date) |>
  dplyr::mutate(n_communities_ge_100 = as.numeric(pm25 >= 100)) |>
  dplyr::group_by(prov_terr, fcst_zone, date) |>
  dplyr::summarise(
    n_sites = n(),
    n_communities_ge_100 = nearest_community[n_communities_ge_100 == 1] |>
      unique() |>
      length(),
    n_sites_above_100 = sum(pm25 >= 100, na.rm = TRUE),
    mean_pm25 = round(mean(pm25, na.rm = TRUE), 1),
    min_pm25 = min(pm25, na.rm = TRUE),
    max_pm25 = max(pm25, na.rm = TRUE)
  ) |>
  dplyr::arrange(
    prov_terr,
    fcst_zone,
    desc(n_sites_above_100),
    desc(n_sites_above_100),
    desc(mean_pm25)
  ) |>
  dplyr::filter(!duplicated(`fcst_zone`)) |>
  dplyr::rename(worst_day = date) |>
  dplyr::mutate(
    n_ge_100 = paste0(
      n_sites_above_100,
      " / ",
      n_sites,
      " (",
      round(n_sites_above_100 / n_sites * 100, 1),
      "%)"
    ),
    worst_day = format(worst_day, "%B %d (%a)")
  ) |>
  dplyr::select(
    "Prov./Terr." = prov_terr,
    "Forecast Zone" = fcst_zone,
    "Worst Day" = worst_day,
    "Sites w/ Daily Mean Above 100 ug/m3" = n_ge_100,
    "Min of Sites" = min_pm25,
    "Mean of Sites" = mean_pm25,
    "Max of Sites" = max_pm25
  )
worst_day_dl2 = pd |>
  download_this(
    output_name = "worst_days_by_fcast_zone_" |>
      paste0(max(obs$date) |> format("%Y-%B")),
    output_extension = ".csv",
    sep = ",",
    dec = ".",
    button_label = "Download data as csv",
    button_type = "default",
    has_icon = TRUE,
    csv2 = FALSE,
    icon = "fa fa-save"
  )
worst_day_table2 = reactable(
  data = pd,
  groupBy = c("Prov./Terr."),
  defaultSorted = "Mean of Sites",
  defaultSortOrder = "desc",
  pagination = FALSE,
  columnGroups = list(
    reactable::colGroup(
      name = "Daily Site Mean PM2.5 Concentration (ug/m3)",
      columns = c("Min of Sites", "Mean of Sites", "Max of Sites")
    )
  )
)
```

```{r analysis7, cache= FALSE}

dat1 = summaries$overall |>
  dplyr::group_by(prov_terr, fcst_zone) |>
  dplyr::summarise(
    pm25_mean_month = mean(pm25_mean, na.rm = TRUE) |> round(1),
    pm25_max_month = max(pm25_max, na.rm = TRUE),
    n_hours_above_60 = max(n_hours_above_60, na.rm = TRUE),
    n_hours_above_100 = max(n_hours_above_100, na.rm = TRUE),
    n_fem = sum(monitor == "FEM"),
    n_pa = sum(monitor == "PA"),
    n_monitors = n(),
    n_communities_w_data = length(unique(nearest_community)),
    n_communities_w_data_mean_ge_100 = nearest_community[pm25_mean >= 100] |>
      unique() |>
      length(),
    n_communities_w_data_max_ge_100 = nearest_community[pm25_max >= 100] |>
      unique() |>
      length(),
    days_w_over_100 = days_w_over_100_max |>
      stringr::str_split(",", simplify = TRUE) |>
      as.vector() |>
      unique() |>
      as.numeric() |>
      sort() |>
      handyr::sentence_range()
  ) |>
  dplyr::left_join(
    fcst_zones |> dplyr::select(fcst_zone, zone_prov = prov_terrs),
    by = "fcst_zone"
  ) |>
  dplyr::mutate(zone_prov = zone_prov |> stringr::str_replace("YT", "YK")) |>
  dplyr::mutate(
    fcst_zone = iconv(fcst_zone, to = "ASCII//TRANSLIT"),
    n_monitors = paste0(n_monitors, " (", n_fem, " FEM, ", n_pa, " PA)"),
    n_communities_w_data_mean_ge_100 = paste(
      n_communities_w_data_mean_ge_100,
      "/",
      n_communities_w_data
    ),
    n_communities_w_data_max_ge_100 = paste(
      n_communities_w_data_max_ge_100,
      "/",
      n_communities_w_data
    )
  ) |>
  dplyr::arrange(desc(n_hours_above_60)) |>
  dplyr::rename(
    "Prov./Terr." = `zone_prov`,
    "Forecast Zone" = fcst_zone,
    "# of Monitors" = n_monitors,
    "1-Month Mean (μg/m3)" = pm25_mean_month,
    "1-Month Max (μg/m3)" = pm25_max_month,
    "# of Communities\nw/ Mean > 100 μg/m3" = n_communities_w_data_mean_ge_100,
    "# of Communities\nw/ Max > 100 μg/m3" = n_communities_w_data_max_ge_100,
    "# Hours above 60 μg/m3" = n_hours_above_60,
    "# Hours above 100 μg/m3" = n_hours_above_100,
    "Day(s) of Month w/\n12+ hours Above 100 μg/m3" = days_w_over_100
  ) |>
  as.data.frame() |>
  dplyr::select(14, 2, 9, 3:4, 5:6, 13)

zone_table <- reactable(
  data = dat1,
  defaultSorted = c("# Hours above 60 μg/m3", "# Hours above 100 μg/m3"),
  defaultSortOrder = "desc",
  defaultPageSize = 15 #,
)
zone_dl <- dat1 |>
  setNames(names(dat1) |> stringr::str_replace_all("\n", " ")) |>
  dplyr::mutate(
    "Day(s) of Month w/ 12+ hours Above 100 μg/m3" = paste0(
      "'",
      `Day(s) of Month w/ 12+ hours Above 100 μg/m3`
    )
  ) |>
  download_this(
    output_name = "fcst_zone_pm25_summaries_" |>
      paste0(output_date_fmt),
    output_extension = ".csv",
    sep = ",",
    button_label = "Download data as csv",
    button_type = "default",
    has_icon = TRUE,
    csv2 = FALSE,
    icon = "fa fa-save"
  )
```

`r if(run_future_month) paste0("<center><h4>**WARNING - This report is incomplete. It only contains data up to ",max(obs$date) |> format("%B %d"),"**</h4></center>") |> HTML()`

## Overview {.unlisted .unnumbered}

`r build_overview_card(type = params$type, report_dropdown = old_report_dropdown)`

`r loading_div`

## Analysis of Past Month of PM~2.5~ Observations

### How many observation sites at each risk level?

`r build_prov_donut_summary(summaries$donuts$data, type = params$type)`

:::: panel-tabset

`r tab_explainers$summary_tabs`

## Max PM~2.5~

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, summaries$donuts$paths$max, quarto_captions$max_donuts, params$type, plot_timestamp = plot_timestamp)`

## Median PM~2.5~

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, summaries$donuts$paths$median, quarto_captions$median_donuts, params$type, plot_timestamp = plot_timestamp)`

::::

### Who had access to nearby observations?

`r build_coverage_summary(coverage_table_data)`

`r tab_explainers$scale_tabs`

`r build_tabs(c("total", "fnic", "urban", "rural"), coverage_table_paths, quarto_captions$coverage, params$type, plot_timestamp = plot_timestamp)`

#### Coverage Table

```{r include = TRUE, cache = FALSE}
coverage_dl
coverage_table
```

### Where and when were PM~2.5~ concentrations high?

`r build_map_summary(summaries$aqhi_p_counts, type = params$type, worst_day = summaries$worst_day)`

`r tab_explainers$scale_tabs`

`r build_tabs(c("daily_zones", "monthly_zones"), list(daily_zones = daily_zone_path, monthly_zones = monthly_zone_path), quarto_captions[c("daily_zones", "monthly_zones")], params$type, plot_timestamp = plot_timestamp, iframe = TRUE, iframe_height = 625)`

### Where and when did PM~2.5~ events occur?

`r tab_explainers$scale_tabs`

:::: panel-tabset

## Province Level

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, prov_grid_paths, quarto_captions$prov_grids, params$type, plot_timestamp = plot_timestamp)`

## Region Level 

`r tab_explainers$prov_terr_tabs`

`r build_tabs(provinces_n_territories, fcst_grid_paths, quarto_captions$zone_grids, params$type, plot_timestamp = plot_timestamp)`

::::

### Which sites had the highest concentrations?

`r build_boxplot_summary(boxplots$summary_values, type = params$type)`  

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, boxplots$paths, quarto_captions$boxplots, params$type, iframe = TRUE, iframe_height = 526, plot_timestamp = plot_timestamp)`

### Which communities [with data] had very high PM~2.5~?

`r build_community_summary(summaries$community, type = params$type)`

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, community_boxplot_paths, quarto_captions$community_boxplots, params$type, iframe = TRUE, iframe_height = 526, plot_timestamp = plot_timestamp)`

### What was the worst day this month? {.panel-tabset}

::: card
::: card-body

**SUMMARY TEXT STILL IN DEVELOPMENT**

:::
:::

`r tab_explainers$scale_tabs`

#### Province Level

::: card

::: {.card-img-top .p-2}

```{r include = TRUE, cache = FALSE}
worst_day_dl
worst_day_table
```

:::

::: card-body

The "worst day" for PM~2.5~ concentrations **for each province**. The "worst day" is determined by the day with the most number of observation sites (FEM or PA) having a daily mean exceeding 100 {{< var units.pm >}} with ties broken by the highest mean of the site daily mean concentrations across the province/territory.

:::

:::

#### Region Level

::: card

::: {.card-img-top .p-2}

```{r include = TRUE, cache=FALSE}
worst_day_dl2
worst_day_table2
```

:::

::: card-body

The "worst day" for PM~2.5~ concentrations **for each forecast zone**. Click on the arrow beside a prov./terr. name to expand the table to view the zones for that area. The "worst day" is determined by the day with the most number of observation sites (FEM or PA) having a daily mean exceeding 100 {{< var units.pm >}} with ties broken by the highest mean of the site daily mean concentrations across the province/territory.

:::

:::

### Which regions were most impacted, and for which days?

::: card
::: card-body

**SUMMARY TEXT STILL IN DEVELOPMENT**

:::
:::

::: card

::: {.card-img-top .p-2}

```{r include = TRUE, cache=FALSE}
zone_dl
zone_table
```

:::

::: card-body

Summary of the PM~2.5~ concentration data within each Canadian forecast zone. The table is interactive, filterable, and has multiple pages. The final column here highlights specific days with high smoke impacts.

:::

:::
