---
params:
  type: "daily"
  default_date: "2026-01-02 00"
  monitor_groups: 
    - "FEM and PA"
    - "FEM" 
    - "PA" 
  dirs:
    value:
      data: data
      plots: plots
      lib: libs
  run_current: false
  report: !expr source("../R/set_params.R"); set_params(type = "daily", default_report_date = "2026-01-02 00")
title: "Canadian PM<sub>2.5</sub> Observations Daily Summary for <mark class='bg-info'>`r params$report$display_name`</mark>"
subtitle: | 
  Non-validated, auto-QA/QCed data representing `r params$report$date_ranges$utc`<br>
  `r params$report$date_ranges$vancouver` in Vancouver |
  `r params$report$date_ranges$halifax` in Halifax
date: "`r params$report$date`"
citation: 
  id: daily-report
  title: "Daily Canada PM2.5 Summary: {RNAME}"
  url: https://aqmap.ca/aqmap/reports/daily/historic/{RFILE}.html
  publisher: "University of Northern British Columbia, Environment and Climate Change Canada"

format:
  html:
    pagetitle: "Daily Canada PM2.5 Summary"
---

<meta name="viewport" content="width=device-width, initial-scale=1">

```{r setup}

source("R/report-functions.R")
source("R/report-constants.R")

all_monitors_group <- params$monitor_groups[1]

old_report_dropdown <- params$type |> build_report_dropdown()

obs <- params$type |>
  get_report_start_end(
    type = params$type,
    run_future = params$run_current,
    default_date = params$default_report_date |> lubridate::ymd_h(tz = "UTC")
  ) |>
  load_report_data(
    meta_cols = meta_cols,
    cache_path = file.path(params$type, "index_obs.rds"), # used when db not available
    provinces_n_territories = provinces_n_territories
  )

date_range <- range(obs$date)
plot_timestamp <- date_range[2] |> format("%F-%Hz")
plot_captions <- date_range |>
  make_plot_captions(networks = params$monitor_groups)
quarto_captions <- date_range |>
  make_quarto_captions(
    monitor_groups = params$monitor_groups,
    all_monitors_group = all_monitors_group
  )

summaries <- obs |>
  make_summaries(
    type = params$type,
    fcst_zones = fcst_zones,
    monitor_groups = params$monitor_groups,
    meta_cols = meta_cols,
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    plot_timestamp = plot_timestamp
  )

```

```{r, overall_summary}

overall_summary_cards <- summaries$overall |>
  make_and_save_overall_summary_cards(
    zone_summary = summaries$by_zone,
    date_range = date_range,
    all_monitors_group = all_monitors_group,
    type = params$type,
    data_dir = params$dirs$data,
    figure_dir = params$dirs$plots,
    lib_dir = params$dirs$lib,
    plot_timestamp = plot_timestamp,
    map_caption = quarto_captions$map,
    table_caption = quarto_captions$table
  )

```

```{r site_boxplots}

boxplots <- summaries$overall |>
  make_and_save_site_boxplots(
    monitor_groups = params$monitor_groups,
    date_range = date_range,
    date_format = "%Y-%m-%d %H:%M (UTC)",
    avg_text = "24-hour",
    plot_timestamp = plot_timestamp,
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    lib_dir = params$dirs$lib
  )

```

```{r grids}

grid_xlab <- "Hour of %s" |> sprintf(format(date_range[2], "%b %d, %Y"))

grid_data <- list(median = median, maximum = max) |>
  lapply(\(FUN) obs |> make_grid_data(FUN = FUN, type = params$type))
prov_grid_paths <- grid_data |>
  make_and_save_prov_terr_grids(
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    monitor_groups = params$monitor_groups,
    plot_timestamp = plot_timestamp,
    xlab = grid_xlab,
    plot_captions = plot_captions
  )

fcst_grid_data <- obs |>
  dplyr::mutate(monitor = all_monitors_group) |>
  make_grid_data(FUN = median, type = params$type, fcst_zones = fcst_zones)
fcst_grid_paths <- fcst_grid_data |>
  make_and_save_fcst_zone_grids(
    report_dir = params$type,
    figure_dir = params$dirs$plots,
    plot_timestamp = plot_timestamp,
    xlab = grid_xlab,
    plot_caption = plot_captions[[all_monitors_group]],
    provinces_n_territories = provinces_n_territories
  )

```

```{r community_summary, include = TRUE}

community_table <- summaries$community |>
  make_community_table(
    type = params$type,
    data_dir = params$dirs$data,
    figure_dir = params$dirs$plots,
    plot_timestamp = plot_timestamp,
    plot_caption = quarto_captions$community_table
  )

```

<!-- Report Start -->

## Overview {.unlisted .unnumbered}

`r build_overview_card(type = params$type, report_dropdown = old_report_dropdown)`

## Past 24-Hours of PM<sub>2.5</sub> Observations

`r build_prov_donut_summary(summaries$donuts$data, type = params$type)`

:::: panel-tabset

`r tab_explainers$summary_tabs`

## Mean PM<sub>2.5</sub>

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, summaries$donuts$paths$median, quarto_captions$median_donuts, params$type, plot_timestamp = plot_timestamp)`

## Max PM<sub>2.5</sub>

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, summaries$donuts$paths$max, quarto_captions$max_donuts, params$type, plot_timestamp = plot_timestamp)`

::::

### Where were PM<sub>2.5</sub> concentrations high?

`r build_map_summary(summaries$aqhi_p_counts, type = params$type)`

`r overall_summary_cards$table`

`r overall_summary_cards$map`

`r build_community_summary(summaries$community, type = params$type)`

`r community_table$card`

### When did PM<sub>2.5</sub> events occur?

`r build_prov_grid_summary(grid_data, type = params$type)`

`r build_fcst_grid_summary(fcst_grid_data, type = params$type)`

`r tab_explainers$scale_tabs`

:::: panel-tabset

## Province Level

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, prov_grid_paths, quarto_captions$prov_grids, params$type, plot_timestamp = plot_timestamp)`

## Region Level 

`r tab_explainers$prov_terr_tabs`

`r build_tabs(provinces_n_territories, fcst_grid_paths, quarto_captions$zone_grids, params$type, plot_timestamp = plot_timestamp)`

::::

### Where were the worst PM<sub>2.5</sub> concentrations?

`r build_boxplot_summary(boxplots$summary_values, type = params$type)`  

`r tab_explainers$network_tabs`

`r build_tabs(params$monitor_groups, boxplots$paths, quarto_captions$boxplots, params$type, iframe = TRUE, iframe_height = 526, plot_timestamp = plot_timestamp)`
